\section{Conclusion}
\label{sec:conclusion}

We presented \prism, a multi-layer runtime defense that combines 
persistent homology, conformal prediction, Bayesian changepoint detection, 
and a topology-aware mixture-of-experts to detect adversarial inputs 
with distribution-free FPR guarantees.
Our experiments on CIFAR-10 demonstrate 100\% TPR against PGD-40,
93\% against Square Attack ($\varepsilon{=}8/255$), and $87\%$ against FGSM ($\varepsilon{=}8/255$)
at FPR$=7.9\%$ ($n=5{,}000$, pooled over 5 seeds), within the conformal guarantee of $\leq10\%$.
The BOCPD campaign detector identifies sustained attacks within 2 adversarial
queries with no false alarm on preceding clean traffic.
The MoE self-healing layer eliminates prediction unavailability for all
L3-triggered adversarials (Recovery$=100\%$ with topology-matched experts).

\paragraph{Limitations.}
The primary limitation is computational: persistent homology over 
high-dimensional activation tensors requires subsampling 
(200 points per layer), which may weaken detection for attacks 
that specifically preserve local topology while altering global structure.
Runtime overhead on CPU is approximately 120\,ms per image (3-layer monitoring);
GPU deployment reduces this to $\sim15$\,ms.
Point-cloud subsampling in \texttt{TopologicalProfiler} uses
deterministic MD5-based hashing (rather than a stateful RNG) to ensure
consistent scoring across calibration and inference passes.
The conformal calibration assumes the clean test distribution matches 
the calibration distribution---distribution shift (e.g., domain adaptation attacks) 
may inflate FPR.

\paragraph{Future work.}
Promising directions include: 
(1) extending to transformer architectures by monitoring 
attention-head activation patterns; 
(2) adaptive $\varepsilon$-free attacks that directly target 
the topological score $S(x)$ as a secondary objective; 
(3) certified robustness integration by combining \prism with 
randomized smoothing \cite{cohen2019certified} for dual guarantees;
(4) adaptive topology attacks that directly target the Wasserstein score $S(x)$
as a secondary optimization objective;
(5) online recalibration to handle distribution shift.

\paragraph{CIFAR-100 generalization.}
Preliminary results find clean FPR$\approx15\%$ on CIFAR-100
(vs. $9\%$ on CIFAR-10), confirming partial generalization of topological
features to fine-grained OOD distributions.
Full cross-dataset evaluation with $n=500$ is planned for the GPU run.

\paragraph{Broader impact.}
\prism is a defensive tool designed to improve the reliability 
of ML systems under adversarial conditions.
We do not foresee misuse potential beyond standard ML security research.
