\section{Introduction}
\label{sec:intro}

Deep neural networks are vulnerable to adversarial examples---inputs crafted 
with small, imperceptible perturbations that cause confident misprediction 
\cite{szegedy2014intriguing,goodfellow2015explaining}.
Despite more than a decade of research, the arms race between attacks and 
defenses remains unresolved: architecturally-coupled defenses require model 
retraining, are often architecture-specific, and may degrade accuracy on clean 
data \cite{croce2020reliable,athalye2018obfuscated}.

A complementary direction is \emph{runtime detection}: rather than hardening 
the model, intercept adversarial inputs before they affect predictions.
Existing detectors often provide no formal statistical guarantees on false 
alarm rates, rely on features that are themselves vulnerable to adaptive 
attacks, or require knowledge of the model's training procedure 
\cite{ma2018characterizing,grosse2017statistical,lee2018simple}.

\textbf{Key insight.} 
Clean and adversarial inputs traverse fundamentally different paths through 
a neural network's activation manifold.
While the output may look confident in both cases, the \emph{topology} of 
intermediate representations---captured by persistent homology---differs 
systematically \cite{gebhart2019adversary,carlini2019evaluating}.
\prism exploits this topological signal at runtime as a 
computationally tractable anomaly score.

\textbf{Contributions.}
We make four contributions:

\begin{enumerate}[leftmargin=*, label=\textbf{C\arabic*}]

\item \textbf{Topological activation profiler (\tamm).}
We compute per-layer Wasserstein distances between input persistence diagrams 
and a reference medoid profile built from clean training data.
This \emph{architecture-agnostic} signature is robust to diverse attack types 
and does not require access to adversarial examples during calibration.

\item \textbf{Conformal detection guarantee (\cadg).}
We apply split conformal prediction to the anomaly score stream, obtaining 
\emph{distribution-free} FPR certificates at three severity tiers 
(L1: $\alpha{=}0.10$; L2: $\alpha{=}0.03$; L3: $\alpha{=}0.005$) 
using only a held-out clean calibration set.

\item \textbf{Temporal campaign detector (\sacd).}
We model the score stream as a Bayesian Online Changepoint Detection (BOCPD) 
problem under a Normal-Inverse-Gamma prior.
When a sustained distribution shift is detected (campaign mode), 
\sacd automatically tightens detection thresholds to improve sensitivity 
against coordinated probing attacks---a threat model absent from prior work.

\item \textbf{Topology-aware MoE recovery (\tamsh).}
For inputs reaching the L3 severity tier, \prism selects the 
topologically-nearest expert sub-network via Wasserstein gating and 
routes the input through it, preserving prediction availability 
rather than issuing a blanket rejection.

\end{enumerate}

Empirically, \prism achieves competitive detection performance against 
FGSM, PGD, C\&W L$_2$, and SquareAttack on CIFAR-10, 
with a 100\% recovery rate for MoE-tier detections.
Our ablation study confirms the contribution of each component.

\textbf{Scope and limitations.}
\prism is a \emph{runtime monitor}, not an adversarial trainer; 
it complements (but does not replace) robust training.
Detection latency scales with the number of monitored layers 
(approximately 0.3\,s per image at 4 layers on CPU); 
GPU deployment reduces this to $<$10\,ms.
Like all detectors, \prism does not provide a guarantee against 
adaptive adversaries who are aware of the topological scoring mechanism.
