\section{Related Work}
\label{sec:related}

\paragraph{TDA for adversarial detection.}
Gebhart and Schrater \cite{gebhart2019adversary} were the first to apply 
persistent homology to adversarial detection, computing topological features 
of neuron activations to distinguish clean from adversarial inputs.
Concurrent work at LANL \cite{lanl2024tda} uses persistent homology with 
two-sample testing for detection in vision-language models.
Goibert et al.\ \cite{goibert2021adversarial} analyze the network graph 
topology of clean vs.\ adversarial inputs.
Relative to these works, \prism's novelty lies in using TDA as the backbone 
of a \emph{full defense pipeline} with formal FPR certificates, 
campaign-level temporal detection, and expert recovery---not as a standalone 
detector.

\paragraph{Conformal prediction for robustness.}
Gendler et al.\ \cite{gendler2022adversarially} (ICLR 2022) combine 
conformal prediction with randomized smoothing to provide adversarially robust 
prediction sets.
Verifiable Robust Conformal Prediction (VRCP) \cite{vrcp2025} uses 
neural network verification to tighten conformal certificates.
Our application of conformal prediction is orthogonal: we use it to calibrate 
a TDA-based \emph{detector} (not a predictor), providing distribution-free FPR 
guarantees on the anomaly score threshold.

\paragraph{Runtime adversarial detectors.}
Feature squeezing \cite{xu2018feature} applies input transformations and 
flags inconsistencies.
Mahala\-nobis detector \cite{lee2018simple} constructs class-conditional 
Gaussians over intermediate representations.
LID \cite{ma2018characterizing} uses local intrinsic dimensionality.
These approaches lack formal coverage guarantees and are vulnerable to 
adaptive attacks that optimize for the same feature space \cite{carlini2017adversarial}.
\prism combines topological features (harder to optimize against) with 
conformal calibration (providing formal guarantees).

\paragraph{Architecture-coupled defenses.}
\rails \cite{wang2022rails} replaces deep network layers with 
topological-nearest neighbor classifiers (DkNN) using topology-preserving 
feature spaces.
Unlike \rails, \prism wraps any pre-trained model without modifying its 
architecture or requiring re-training.
Input purification methods \cite{shi2021online,yoon2021adversarial} 
apply preprocessing but require end-to-end access to the classifier.

\paragraph{Temporal adversarial defense.}
Despite extensive work on temporal adversarial attacks 
\cite{temporal2026survey}, session-level adversarial campaign \emph{detection} 
in neural network inference pipelines remains underexplored.
\sacd is, to our knowledge, the first to apply BOCPD to runtime adversarial 
campaign monitoring.
